---
title: "MovieRatingAnalysis"
author: "18F-0387"
date: "11/19/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(ggplot2)
library(ggthemes)
library(scales)
library(dplyr)
library(lessR)
```

-extracting data from .dat file where seperator is '::'
-making extracted data a dataframe
-displaying its top 6 rows
```{r}
MOVIE_DATASET = do.call(rbind,strsplit(readLines('C:/Users/Talha/Downloads/movies.dat'),'::',fixed=T))
MOVIE_DATASET <- as.data.frame(MOVIE_DATASET)
head(MOVIE_DATASET)
```

-assigning column names to dataframe
-making ID column numeric
-displaying its top 6 rows
```{r}
colnames(MOVIE_DATASET) <- c("ID","Title","Genre")
MOVIE_DATASET$ID <- as.numeric(MOVIE_DATASET$ID)
head(MOVIE_DATASET)
```

-extracting data from .dat file where seperator is '::'
-displaying its top 6 rows
```{r}
Rating_of_movies = read.delim("ratings.dat", header= FALSE ,sep = ':', colClasses = c(NA, "NULL"))
head(Rating_of_movies)
```
-assigning column names to dataframe
-making ID column numeric
-displaying its top 6 rows
```{r}
colnames(Rating_of_movies) <- c("User","ID","Rating_of_movies","Timestamp")
head(Rating_of_movies)
```

-merging dataframes based on ID
-displaying its top 6 rows
```{r}
data = merge(MOVIE_DATASET,Rating_of_movies,by = "ID")
data = data[with(data, order(ID)),]
head(data)
```

-ploting pie chart
```{r}
Rating_of_movies<- dplyr::count(data, Rating_of_movies, sort = TRUE) %>% 
  mutate(perc = `n` / sum(`n`)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))

ggplot(Rating_of_movies, aes(x = "", y = perc, fill = factor(Rating_of_movies)),alpha = 0.8) +
  geom_col() +
  geom_text(aes(label = labels),
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y")
```

